---
title: "Regress-General usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette will explain how to use the package for fitting both Simple Linear Regression (SLR) and Multiple Linear Regression (MLR) models using a simulated data. Begin by loading the package and setting a seed for reproducibility.
```{r setup}
library(Regress)
set.seed(700)
```

We will first simulate a data to fit the models. This data contains two predictor variables($X_{1}, X_{2}$) and a response variable ($Y$).
```{r}
# Define parameters
n = 100
a = -3
b = 2
c = 4
error_std = 7
# Generate x values
X1 = runif(n, min = -25, max = 25)
X2 = runif(n, min = -25, max = 25)
# Define the error term
epsilon = rnorm(n, 0, error_std)
# Compute the y values
Y = c + a*X1 + b*X2 + epsilon
# Combine them to get the dataset
Data = data.frame(X1 = X1, X2 = X2, Y = Y)
attach(Data)
head(Data)
```

Next, we'll fit a simple linear regression model with one of the predictors. The predictor variable has to be a column vector.
```{r}
X = cbind(X1)
model1 = JusticeRegress(Y = Y,X =X)
model1
```
We will also fit a multiple linear regression model with the dataset. You will need to pass just one X in the function, so you need to make X a matrix with each column a different variable.
```{r}
X = cbind(X1,X2)
model2 = JusticeRegress(Y = Y, X = X)
model2
```

# Comparison of the results from SLR model with the lm() function
Here, we compare the results from the two models with lm() function using all.equal() to demonstrate correctness of the JusticeRegress function. Let us compare the estimates from the SLR models.

```{r}
# Fit the SLR with the lm() function
lm_model1 = lm(Y~X1, data = Data)
```

We used as.matrix() because because coef(summary(lm_model1)) returns a matrix. Set "check.attributes = FALSE" because the outputs have different names/attributes.
```{r}
all.equal(coef(summary(lm_model1)),as.matrix(model1$Estimates), check.attributes=FALSE)
```
Let us use "bench::mark" to compare the efficiency of JusticeRegress() and lm(). The numeric values are the same (ignoring the attributes), so we set "check=FALSE" here to ignore the attributes.
```{r}
benchmark1 = bench::mark(
 my_fun = model1$Estimates, 
 lm_fun =  coef(summary(lm_model1)), 
 iterations = 100,
 check = FALSE
)
# Print the result
print(benchmark1)
```
# Comparison of the results from MLR model with the lm() function
We compare the estimates from the MLR models.
```{r}
# Fit the MLR with the lm() function
lm_model2 = lm(Y~X1+X2, data = Data)
all.equal(coef(summary(lm_model2)),as.matrix(model2$Estimates), check.attributes=FALSE)
```

Comparing the efficiency between the two fits
```{r}
benchmark2 = bench::mark(
 my_fun = model2$Estimates, 
 lm_fun =  coef(summary(lm_model2)), 
 iterations = 100,
 check = FALSE
)
# Print the result
print(benchmark2)
```
